### 2020-03-06 short.body.tex
push

To begin, consider a renewal equation variant in which incidence $i$ is divided into two categories -- $i_a$ and $i_s$ -- corresponding to incidence of asymptomatic and symptomatic cases, respectively. 
Both types of individuals can infect others, but, they differ in their intrinsic reproduction numbers, ${\cal{R}}_a$ and ${\cal{R}}_s$, as well as intrinsic generation-interval distributions, $g_a(\tau)$ and $g_s(\tau)$, reflecting their differences in the abilities to transmit and the courses of infection.
Generation intervals, which are defined as the time between when an individual is infected and when that individual infects another person, depend on the natural history of infection:
an individual with subclinical, and fast-clearing, symptoms is likely to have short generation intervals, whereas an individual with mild, but long-lasting, symptoms is likely to have long generation intervals.
In total, the dynamics of susceptibles and incidence are:
\begin{eqnarray}
\dot{S}&=&-i(t) \\
i(t)&=&\mathcal R_a S \int_0^\infty i_a(t-\tau) g_a(\tau) \mathrm{d}\tau + \mathcal R_s S \int_0^\infty i_s(t-\tau) g_s(\tau) \mathrm{d}\tau.
\end{eqnarray}
Here, $p$ is the fraction of asymptomatic cases that are generated for each infected individual ($i_a(t)= p i(t)$), and $1-p$ is the fraction of symptomatic cases that are generated for each infected individual ($i_s(t)= (1-p) i(t)$).

@@

The basic reproduction number, ${\cal{R}}_0$, characterize the strength of an epidemic in an otherwise susceptible population:
\begin{equation}
{\cal{R}}_{0}= p {\cal{R}}_a + (1-p) {\cal{R}}_s.
\end{equation}
Then, the \emph{intrinsic} proportion of asymptomatic $z$ and symptomatic $1-z$ transmission is equal to their relative contribution toward the basic reproduction number, 
\begin{eqnarray}
z &=& p {\cal{R}}_a/{\cal{R}}_{0},\\
1-z &=& (1-p) {\cal{R}}_s/{\cal{R}}_{0}.
\end{eqnarray}
Then, the \emph{intrinsic} generation-interval distribution depends on the intrinsic proportion of asymptomatic vs.~symptomatic transmission and their corresponding \emph{intrinsic} generation-interval distributions:
\begin{equation}
g(\tau) = z g_a(\tau) + (1-z) g_s(\tau),
\end{equation}
which allows us to express incidence of infection as a renewal process that depends on previous incidence:
\begin{equation}
i(t) = {\cal{R}}_{0} \int_0^\infty i(t-\tau) g(\tau) \mathrm{d} \tau.
\end{equation}
Yet, this information is not sufficient to disentangle the role of asymptomatic cases, i.e., what fraction of secondary cases can be ascribed to \emph{realized} transmission from asymptomatic cases vs.~symptomatic cases?

@@

Here, given $1/r=7$ days, $\bar G_s=6$ days, and $\kappa_s=0.5$, we evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection, given variation in relative mean generation interval $\bar G_a/\bar G_s$ and relative generation-interval dispersion $\kappa_a/\kappa_s$ of asymptomatic cases.
We vary $\bar G_a/\bar G_s$ and $\kappa_a/\kappa_s$ from 0.5 to 1.5, one at a time, and infer $q$ as well as ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and asymptomatic cases.
Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A,C).
When the mean asymptomatic generation interval is longer than the mean symptomatic generation interval, $q$ decreases because short generation intervals (i.e., fast transmission) caused by symptomatic individuals drive the transmission during the growth phase.
On the other hand, assuming a wide generation-interval distribution (higher $\kappa_a$) for asymptomatic individuals increases $q$ because the amount of short generation intervals (i.e., the proportion of faster transmission by asymptomatic individuals) increases.

Figure~\ref{fig.relevance}C shows that when $\bar G_s<\bar G_a$, then the strength ${\cal{R}}_0$ increases with $z$.
This increase arises because asymptomatic infections that have long generation intervals increase the duration of overall generation intervals (see~\citep{park_2019practical})
Conversely, when $\bar G_a > \bar G_s$ then the strength ${\cal{R}}_0$ decreases with $z$ because short generation intervals of asymptomatic cases reduce the overall mean generation interval.
Likewise, the amount of dispersion in the generation intervals of asymptomatic cases $\kappa_a$ affect the amount of dispersion in the overall generation intervals; 
therefore, depending on whether $\kappa_a$ is larger or smaller than $\kappa_s$, increase in the proportion of asymptomatic transmission $z$ can either decrease or increase the strength ${\cal{R}}_0$.
In other words, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative mean and dispersion in generation intervals of asymptomatic and symptomatic individuals.

>>>>

To begin, consider a renewal equation variant in which incidence $i$ is divided into two categories -- $i_a$ and $i_s$ -- corresponding to incidence of asymptomatic and symptomatic cases, respectively. 
Both types of individuals can infect others, but, they differ in their intrinsic reproduction numbers, ${\cal{R}}_a$ and ${\cal{R}}_s$, as well as intrinsic generation-interval distributions, $g_a(\tau)$ and $g_s(\tau)$, reflecting their differences in the abilities to transmit and the courses of infection.
Generation intervals, which are defined as the time between when an individual is infected and when that individual infects another person \citep{svensson2007note}, depend on the natural history of infection:
an individual with subclinical, and fast-clearing, symptoms is likely to have short generation intervals, whereas an individual with mild, but long-lasting, symptoms is likely to have long generation intervals.
In total, the dynamics of susceptibles and incidence are:
\begin{eqnarray}
\dot{S}&=&-i(t) \\
i(t)&=&\mathcal R_a S \int_0^\infty i_a(t-\tau) g_a(\tau) \mathrm{d}\tau + \mathcal R_s S \int_0^\infty i_s(t-\tau) g_s(\tau) \mathrm{d}\tau.
\end{eqnarray}
Here, $p$ is the fraction of asymptomatic cases that are generated for each infected individual ($i_a(t)= p i(t)$), and $1-p$ is the fraction of symptomatic cases that are generated for each infected individual ($i_s(t)= (1-p) i(t)$).

@@

The basic reproduction number, ${\cal{R}}_0$, characterize the strength of an epidemic in an otherwise susceptible population \citep{anderson1992infectious}:
\begin{equation}
{\cal{R}}_{0}= p {\cal{R}}_a + (1-p) {\cal{R}}_s.
\end{equation}
Then, the \emph{intrinsic} proportion of asymptomatic $z$ and symptomatic $1-z$ transmission is equal to their relative contribution toward the basic reproduction number, 
\begin{eqnarray}
z &=& p {\cal{R}}_a/{\cal{R}}_{0},\\
1-z &=& (1-p) {\cal{R}}_s/{\cal{R}}_{0}.
\end{eqnarray}
Then, the \emph{intrinsic} generation-interval distribution depends on the intrinsic proportion of asymptomatic vs.~symptomatic transmission and their corresponding \emph{intrinsic} generation-interval distributions:
\begin{equation}
g(\tau) = z g_a(\tau) + (1-z) g_s(\tau),
\end{equation}
which allows us to express incidence of infection as a renewal process that depends on previous incidence:
\begin{equation}
i(t) = {\cal{R}}_{0} \int_0^\infty i(t-\tau) g(\tau) \mathrm{d} \tau.
\end{equation}
Yet, this information is not sufficient to disentangle the role of asymptomatic cases, i.e., what fraction of secondary cases can be ascribed to \emph{realized} transmission from asymptomatic cases vs.~symptomatic cases?

@@

Here, given $1/r=7$ days, $\bar G_s=6$ days, and $\kappa_s=0.5$, we evaluate the impacts of intrinsic proportion of asymptomatic transmission $z$ on the realized relevance of asymptomatic infection, given variation in relative mean generation interval $\bar G_a/\bar G_s$ and relative generation-interval dispersion $\kappa_a/\kappa_s$ of asymptomatic cases.
We vary $\bar G_a/\bar G_s$ and $\kappa_a/\kappa_s$ between 0.5 and 1.5 one at a time, and infer $q$ and ${\cal{R}}_0$ compatible with an estimated value of $r$ from case data given the generation interval distributions of asymptomatic and asymptomatic cases.
Across the ranges of parameters we explore, the intrinsic proportion of asymptomatic transmission $z$ is similar to the realized proportion $q$ (Figure~\ref{fig.relevance}A,C).
When the mean asymptomatic generation interval is longer than the mean symptomatic generation interval, $q$ decreases because short generation intervals (i.e., fast transmission) caused by symptomatic individuals drive the transmission during the growth phase (Figure~\ref{fig.relevance}A).
On the other hand, assuming a wide generation-interval distribution (higher $\kappa_a$) for asymptomatic individuals increases $q$ because the amount of short generation intervals (i.e., the proportion of faster transmission by asymptomatic individuals) increases (Figure~\ref{fig.relevance}C).

Figure~\ref{fig.relevance}C shows that when $\bar G_s<\bar G_a$, then the strength ${\cal{R}}_0$ increases with $z$.
This increase arises because asymptomatic infections that have long generation intervals increase the duration of overall generation intervals (see~\citep{park_2019practical})
Conversely, when $\bar G_a > \bar G_s$ then the strength ${\cal{R}}_0$ decreases with $z$ because short generation intervals of asymptomatic cases reduce the overall mean generation interval.
Likewise, the amount of dispersion in the generation intervals of asymptomatic cases $\kappa_a$ affect the amount of dispersion in the overall generation intervals; 
therefore, depending on whether $\kappa_a$ is larger or smaller than $\kappa_s$, increase in the proportion of asymptomatic transmission $z$ can either decrease or increase the strength ${\cal{R}}_0$ (Figure~\ref{fig.relevance}D).
In other words, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread, it can be over- or under- estimated depending on the relative mean and dispersion in generation intervals of asymptomatic and symptomatic individuals.
